---
title: "Linear Models"
author:  "Alexey Abramov"
date: "11/23/2020"
output: 
  github_document:
    toc: true
---

# Setup

```{r, setup}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%"
)

theme_set(
  ggthemes::theme_fivethirtyeight() + theme(legend.position = "bottom")
  )

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.colour = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Loading the data.

```{r}
data("nyc_airbnb")

nyc_airbnb =
  nyc_airbnb %>% 
    mutate(
      stars = review_scores_location/ 2) %>% 
  rename(
      borough = neighbourhood_group,
      neighborhood = (neighbourhood)) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

# Fit a Model

```{r}
nyc_airbnb %>%  
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

```{r}
airbnbn_price_fit = lm(price ~ stars + borough, data = nyc_airbnb)
summary(airbnbn_price_fit)
```

Better way to do it?
```{r}
broom::glance(airbnbn_price_fit)
```

Another good way
```{r}
broom::tidy(airbnbn_price_fit) %>% 
  select(-std.error, -statistic) %>% 
  mutate(
    term = str_replace(term, "borough", "Borough = ")) %>% 
      knitr::kable(digits = 3)
```

## Be in control of factors

Note that the Bronx is the reference group... because it's in alphabetical order... and that's bcause borough is a character.

How do we do it so the most common borough? Instead of alphabetical
```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
    )

```

```{r}
nyc_airbnb %>%  
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

So now we can see that the reference group is Manhattan, and not the Bronx!  A more plausible group.  

```{r}
airbnbn_price_fit2 = lm(price ~ stars + borough, data = nyc_airbnb)
broom::tidy(airbnbn_price_fit2)
```

